Human Factors Influencing Visual Statistical Inference

### 2015-08-30 sociology_paper.Rnw
getting fp7 to converge
table 5 to confidence intervals

\subsection{Demographic Factors}  %In addition to obtain evaluation responses of the lineups, all the 10 experiments shown in Table~\ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:
\noindent
For all  ten experiments shown in Table~\ref{tbl:visual_stat}, the following demographic information was collected from subjects:

@@

\cline{3-6} \cline{8-11} 
\multicolumn{2}{c}{{Demographic Factor} \hfill Level} & Est & 2.5\% & 97.5\% &   && Est & 2.5\% & 97.5\% &   \\ 
\cline{3-6} \cline{8-11}
\bf Fixed Effects & Average $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.61 & -0.79 & -0.43 & *** \\ [3pt]
\bf Age Category $(\alpha)$ & 18-25 & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  26-30 & 0.06 & 0.03 & 0.08 & *** &   & 0.06 & -0.03 & 0.16 &  \\ 
&  31-35 & 0.07 & 0.04 & 0.10 & *** &   & 0.11 & 0.01 & 0.22 & * \\ 
&  36-40 & 0.23 & 0.20 & 0.26 & *** &   & 0.31 & 0.19 & 0.43 & *** \\ 
&  41-45 & 0.18 & 0.14 & 0.22 & *** &   & 0.16 & 0.00 & 0.31 & * \\ 
&  46-50 & 0.27 & 0.22 & 0.32 & *** &   & 0.14 & -0.05 & 0.33 &  \\ 
&  above 50 & 0.35 & 0.32 & 0.39 & *** &   & 0.15 & 0.01 & 0.28 & * \\ [3pt]
\bf Country $(\kappa)$& U.S. & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  India & 0.23 & 0.21 & 0.25 & *** &   & -0.18 & -0.27 & -0.10 & *** \\ 
&  Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.08 & -0.04 & 0.20 &  \\ [3pt]
\bf Education $(\tau)$& High School & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & -0.03 & -0.18 & 0.11 &  \\ 
&  Under grad degree & 0.13 & 0.10 & 0.17 & *** &   & 0.12 & -0.01 & 0.26 & . \\ 
&  Graduate courses & 0.01 & -0.04 & 0.05 &  &   & -0.17 & -0.33 & -0.01 & * \\ 
&  Graduate degree & 0.13 & 0.09 & 0.16 & *** &   & -0.06 & -0.19 & 0.07 &  \\ [3pt]
\bf Gender $(\gamma)$& Female & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Male & 0.08 & 0.06 & 0.10 & *** &   & 0.06 & -0.02 & 0.13 &  \\
\cline{3-6} \cline{8-11}
\bf Random Effects &  lineup $(\sigma_\ell)$& \multicolumn{5}{l}{0.29} & \multicolumn{4}{l}{\phantom{-}2.29} \\ 
                   &  Error $(\sigma)$& \multicolumn{5}{l}{0.69} & \multicolumn{4}{l}{\phantom{-}0.89}  \\ 
\cline{3-6} \cline{8-11}
\end{tabular}}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{0.81}{
\begin{tabular}{rrrrccrrrccrrrc}
  \hline
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\

\cline{2-5} \cline{7-10} \cline{12-15} 
 Effect& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value \\ 
  \hline
Fixed &  &  &  & && &  & & & & & &  & \\ 
$\mu$ & -1.304 & 0.179 & -7.28 & $<$0.001 &   & -0.220 & 0.147 & -1.50 & 0.134 &   & -1.737 & 0.481 & -3.61 & $<$0.001 \\ 
  $\alpha_1$ & 0.000 & --- & --- & --- &   & 0.000 & --- & --- & --- &  & 0.000 & --- & --- & ---  \\ 
  $\alpha_2$ & 0.270 & 0.219 & 1.24 & 0.217 &   & 0.262 & 0.158 & 1.66 & 0.098 &   & -0.456 & 0.385 & -1.18 & 0.237 \\ 
  $\alpha_3$ & -0.178 & 0.226 & -0.79 & 0.432 &   & 0.342 & 0.157 & 2.18 & 0.029 &   & -0.105 & 0.386 & -0.27 & 0.786 \\ 
  $\alpha_4$ & 0.083 & 0.224 & 0.37 & 0.712 &   & 0.358 & 0.159 & 2.26 & 0.024 &   & -0.378 & 0.381 & -0.99 & 0.322 \\ 
  $\alpha_5$ & 0.298 & 0.224 & 1.33 & 0.183 &   & 0.376 & 0.159 & 2.36 & 0.018 &   & -0.107 & 0.385 & -0.28 & 0.781 \\ 
  $\alpha_6$ & 0.042 & 0.231 & 0.18 & 0.857 &   & 0.246 & 0.158 & 1.56 & 0.120 &   & 0.026 & 0.407 & 0.06 & 0.949 \\ 
  $\alpha_7$ & 0.283 & 0.230 & 1.23 & 0.217 &   & 0.160 & 0.159 & 1.01 & 0.314 &   & 0.057 & 0.401 & 0.14 & 0.886 \\ 
  $\alpha_8$ & -0.045 & 0.233 & -0.19 & 0.847 &   & 0.341 & 0.160 & 2.13 & 0.033 &   & -0.003 & 0.394 & -0.01 & 0.994 \\ 
  $\alpha_9$ & -0.195 & 0.232 & -0.84 & 0.400 &   & 0.378 & 0.160 & 2.36 & 0.018 &   & 0.204 & 0.436 & 0.47 & 0.639 \\ 
  $\alpha_{10}$ & 0.513 & 0.228 & 2.25 & 0.024 &   & 0.192 & 0.163 & 1.18 & 0.238 &   & -0.213 & 0.432 & -0.49 & 0.622 \\ 
\multicolumn{2}{l}{Random}   &  &  &  &  & & &&& & & &  & \\ 
  $\sigma^2_a$ &  0.017 &&  &  &   &  0.034 &&  &  &   &  0.163 &&  &  \\ 
  $\sigma^2_u$  & 0.848 &&  &  &    & 0.903 &&  &  &   &  $<$0.001 &&  &  \\ 
  $\sigma^2_{\ell}$  & 1.476 &&  &  &    & 1.418 &&  &  &   &  3.314 &&  &  \\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_response}
\end{table}

>>>>

\subsection{Demographic Factors}  %In addition to obtain evaluation responses of the lineups, all the 10 experiments shown in Table~\ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:
\hh{XXX compare demographics to US Census data - we see relatively young, relatively highly educated participants compared to general population. Being amazon turkers implicitly assures a relatively high level of technological fluency. }
\noindent
For all  ten experiments shown in Table~\ref{tbl:visual_stat}, the following demographic information was collected from subjects:

@@

\cline{3-6} \cline{8-11} 
\multicolumn{2}{c}{{Demographic Factor} \hfill Level} & Est & 2.5\% & 97.5\% &   && Est & 2.5\% & 97.5\% &   \\ 
\cline{3-6} \cline{8-11}
\bf Fixed Effects & Average $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.61 & -0.79 & -0.43 & *** \\ [3pt]
\bf Age Category $(\alpha)$ & 18-25 & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  26-30 & 0.06 & 0.03 & 0.08 & *** &   & 0.06 & -0.03 & 0.16 &  \\ 
&  31-35 & 0.07 & 0.04 & 0.10 & *** &   & 0.11 & 0.01 & 0.22 & * \\ 
&  36-40 & 0.23 & 0.20 & 0.26 & *** &   & 0.31 & 0.19 & 0.43 & *** \\ 
&  41-45 & 0.18 & 0.14 & 0.22 & *** &   & 0.16 & 0.00 & 0.31 & * \\ 
&  46-50 & 0.27 & 0.22 & 0.32 & *** &   & 0.14 & -0.05 & 0.33 &  \\ 
&  above 50 & 0.35 & 0.32 & 0.39 & *** &   & 0.15 & 0.01 & 0.28 & * \\ [3pt]
\bf Country $(\kappa)$& U.S. & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  India & 0.23 & 0.21 & 0.25 & *** &   & -0.18 & -0.27 & -0.10 & *** \\ 
&  Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.08 & -0.04 & 0.20 &  \\ [3pt]
\bf Education $(\tau)$& High School & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & -0.03 & -0.18 & 0.11 &  \\ 
&  Under grad degree & 0.13 & 0.10 & 0.17 & *** &   & 0.12 & -0.01 & 0.26 & . \\ 
&  Graduate courses & 0.01 & -0.04 & 0.05 &  &   & -0.17 & -0.33 & -0.01 & * \\ 
&  Graduate degree & 0.13 & 0.09 & 0.16 & *** &   & -0.06 & -0.19 & 0.07 &  \\ [3pt]
\bf Gender $(\gamma)$& Female & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Male & 0.08 & 0.06 & 0.10 & *** &   & 0.06 & -0.02 & 0.13 &  \\
\cline{3-6} \cline{8-11}
\bf Random Effects &  lineup $(\sigma_\ell)$& \multicolumn{5}{l}{0.29} & \multicolumn{4}{l}{\phantom{-}2.29} \\ 
                   &  Error $(\sigma)$& \multicolumn{5}{l}{0.69} & \multicolumn{4}{l}{\phantom{-}0.89}  \\ 
\cline{3-6} \cline{8-11}\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}

@@

% \begin{table}[htbp]
% \centering
% \caption{Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
% \scalebox{0.81}{
% \begin{tabular}{rrrrccrrrccrrrc}
%   \hline
% & \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
% 
% \cline{2-5} \cline{7-10} \cline{12-15} 
%  Effect& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value \\ 
%   \hline
% Fixed &  &  &  & && &  & & & & & &  & \\ 
% $\mu$ & -1.304 & 0.179 & -7.28 & $<$0.001 &   & -0.220 & 0.147 & -1.50 & 0.134 &   & -1.737 & 0.481 & -3.61 & $<$0.001 \\ 
%   $\alpha_1$ & 0.000 & --- & --- & --- &   & 0.000 & --- & --- & --- &  & 0.000 & --- & --- & ---  \\ 
%   $\alpha_2$ & 0.270 & 0.219 & 1.24 & 0.217 &   & 0.262 & 0.158 & 1.66 & 0.098 &   & -0.456 & 0.385 & -1.18 & 0.237 \\ 
%   $\alpha_3$ & -0.178 & 0.226 & -0.79 & 0.432 &   & 0.342 & 0.157 & 2.18 & 0.029 &   & -0.105 & 0.386 & -0.27 & 0.786 \\ 
%   $\alpha_4$ & 0.083 & 0.224 & 0.37 & 0.712 &   & 0.358 & 0.159 & 2.26 & 0.024 &   & -0.378 & 0.381 & -0.99 & 0.322 \\ 
%   $\alpha_5$ & 0.298 & 0.224 & 1.33 & 0.183 &   & 0.376 & 0.159 & 2.36 & 0.018 &   & -0.107 & 0.385 & -0.28 & 0.781 \\ 
%   $\alpha_6$ & 0.042 & 0.231 & 0.18 & 0.857 &   & 0.246 & 0.158 & 1.56 & 0.120 &   & 0.026 & 0.407 & 0.06 & 0.949 \\ 
%   $\alpha_7$ & 0.283 & 0.230 & 1.23 & 0.217 &   & 0.160 & 0.159 & 1.01 & 0.314 &   & 0.057 & 0.401 & 0.14 & 0.886 \\ 
%   $\alpha_8$ & -0.045 & 0.233 & -0.19 & 0.847 &   & 0.341 & 0.160 & 2.13 & 0.033 &   & -0.003 & 0.394 & -0.01 & 0.994 \\ 
%   $\alpha_9$ & -0.195 & 0.232 & -0.84 & 0.400 &   & 0.378 & 0.160 & 2.36 & 0.018 &   & 0.204 & 0.436 & 0.47 & 0.639 \\ 
%   $\alpha_{10}$ & 0.513 & 0.228 & 2.25 & 0.024 &   & 0.192 & 0.163 & 1.18 & 0.238 &   & -0.213 & 0.432 & -0.49 & 0.622 \\ 
% \multicolumn{2}{l}{Random}   &  &  &  &  & & &&& & & &  & \\ 
%   $\sigma^2_a$ &  0.017 &&  &  &   &  0.034 &&  &  &   &  0.163 &&  &  \\ 
%   $\sigma^2_u$  & 0.848 &&  &  &    & 0.903 &&  &  &   &  $<$0.001 &&  &  \\ 
%   $\sigma^2_{\ell}$  & 1.476 &&  &  &    & 1.418 &&  &  &   &  3.314 &&  &  \\ 
%    \hline
% \end{tabular}
% }
% \label{tbl:model_result_response}
% \end{table}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:15:41 2015
\begin{table}[hbtp]
\centering
\caption{\label{tbl:model_result_response}Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows some evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{.81}{
\begin{tabular}{rr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
\cline{2-5} \cline{7-10} \cline{12-15} 
Effect & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
Fixed \\
$\mu$ & -1.30 & -1.69 & -0.92 & *** &   & -0.22 & -0.51 & 0.07 &  &   & -1.71 & -2.77 & -0.65 & ** \\ [3pt]
  $\alpha_2$ & 0.27 & -0.19 & 0.73 &  &   & 0.26 & -0.06 & 0.58 &  &   & -0.49 & -1.31 & 0.32 &  \\ 
  $\alpha_3$ & -0.18 & -0.65 & 0.29 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.19 & -1.01 & 0.63 &  \\ 
  $\alpha_4$ & 0.08 & -0.39 & 0.55 &  &   & 0.36 & 0.04 & 0.68 & * &   & -0.47 & -1.28 & 0.35 &  \\ 
  $\alpha_5$ & 0.30 & -0.17 & 0.77 &  &   & 0.37 & 0.05 & 0.70 & * &   & -0.16 & -0.96 & 0.65 &  \\ 
  $\alpha_6$ & 0.04 & -0.44 & 0.53 &  &   & 0.24 & -0.07 & 0.56 &  &   & -0.03 & -0.87 & 0.82 &  \\ 
  $\alpha_7$ & 0.28 & -0.20 & 0.77 &  &   & 0.16 & -0.16 & 0.48 &  &   & 0.02 & -0.81 & 0.84 &  \\ 
  $\alpha_8$ & -0.04 & -0.54 & 0.45 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.08 & -0.89 & 0.73 &  \\ 
  $\alpha_9$ & -0.20 & -0.69 & 0.30 &  &   & 0.38 & 0.05 & 0.70 & * &   & 0.15 & -0.71 & 1.02 &  \\ 
  $\alpha_{10}$ & 0.51 & 0.03 & 1.00 & * &   & 0.19 & -0.14 & 0.52 &  &   & -0.28 & -1.14 & 0.58 &  \\ 
  Random \\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.85}  & \multicolumn{5}{l}{\phantom{-}0.90} & 0.76   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.02}  & \multicolumn{5}{l}{\phantom{-}0.03} & 0.06   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}1.48}  & \multicolumn{5}{l}{\phantom{-}1.42} & 3.37   \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
\end{tabular}}
\end{table}
